Differentially Private Bayesian Inference

### 2018-07-08 main-sketch.tex
updates

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism. In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d. Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. The private posterior then will be $\dirichlet(\alpha_1 + n_1 + , \alpha_2 + n_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_prior_5_5_5}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_vs_prior_variance}
\end{figure}

>>>>

Then we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$. When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance. We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism. In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d. Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. The private posterior then will be $\dirichlet(\alpha_1 + n_1 + | Lap_1 |, \alpha_2 + n_2 + | Lap_2 |, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_vs_prior_5_5_5}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{Accuracy_VS_Prior_mean.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
\label{fig_vs_prior_variance}
\end{figure}
